FoRTE Disturbance Paper Analysis

### 2021-06-28 C.analysis/paper_analysis.Rmd
pre co-author feedback

library(dplyr)
library(ggplot2)
library(stringr)

@@

@@

@@

@@

```{r, fig.width=5, fig.height=5}
resilience %>% 
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.75, size = 1.5) + 
  facet_wrap("variable", scales = "free",  
             labeller = label_glue('({.l}) {variable}')) + 
  labs(x = "Resistance", 
       y = "Resilience", 
       title = "Resilience vs. Resistance") + 
  theme_bw(base_size = 10) +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  guides(colour = guide_legend("Severity")) -> 
  plot

@@

>>>>

library(dplyr)
library(ggplot2)
library(stringr)
library(stickylabeller)
library(ggpmisc)
library(ggpubr)

@@

```{r}
ED_output %>%  
  filter(scn == "harvest_0" & variable  %in% c("GPP", "NPP", "Rh", "NEP", "AGB")) %>% 
  mutate(description = paste0(variable, '\n (', unit,  ')')) %>% 
  dplyr::filter(year == 2020) %>% 
  group_by(variable, unit) %>% 
  summarise(sd = sd(value), mean = mean(value)) %>% 
  ungroup %>% 
  mutate(cv = sd/mean)

@@

```{r}

resistance %>% 
  group_by(variable, severity) %>%  
  summarise(mean = mean(trough_resistance), sd = sd(trough_resistance))

@@

```{r}
resilience %>% 
  group_by(variable, severity) %>% 
  summarise(mean = mean(resilience))

@@

```{r, fig.width=5, fig.height=5}
resilience %>% 
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.75, size = 1.5) + 
  facet_wrap("variable", #scales = "free",  
             labeller = label_glue('({.l}) {variable}')) + 
  labs(x = "Resistance", 
       y = "Resilience", 
       title = "Resilience vs. Resistance") + 
  theme_bw(base_size = 10) +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  guides(colour = guide_legend("Severity")) -> 
  plot

@@

```{r, fig.width=5, fig.height=5}
my.formula <- y ~ x

resilience %>% 
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.75, size = 1.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.2) + 
  stat_cor(method = "pearson", aes(label = ..r.label..),
           size = 3, label.x.npc = "left", label.y.npc = "bottom", 
           r.accuracy = 0.01) + 
  labs(x = "Resistance", 
       y = "Resilience", 
       title = "Resilience vs. Resistance") + 
  theme_bw(base_size = 10) +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
    facet_wrap("variable", scales = "free",  
            labeller = label_glue('({.l}) {variable}')) + 
  guides(colour = guide_legend("Severity")) +
  ggsave("figures/resistance_resilience3.png", width = 6, height = 4.5)

```{r}

resilience %>% 
  left_join(resistance) %>%  
  ggplot(aes(trough_resistance, resilience, color = severity)) + 
  geom_point(alpha = 0.75, size = 1.5) + 
  geom_smooth(method = "lm", size = 0.5, alpha = 0.2) + 
  stat_cor(method = "pearson", aes(label = ..r.label..),
           size = 3, label.x.npc = "left", label.y.npc = "bottom", 
           r.accuracy = 0.01) + 
  labs(x = "Resistance", 
       y = "Resilience", 
       title = "Resilience vs. Resistance") + 
  theme_bw(base_size = 10) +
  scale_color_manual(values = FORTE_SEVERITY_COLORS) + 
  guides(colour = guide_legend("Severity"))
